---
title: "p8105_hw5_wm2473"
output: github_document
date: "2022-11-14"
---

```{r}
library(tidyverse)
library(readxl)
library(rvest)
library(ggplot2)
set.seed(1)

```

Problem 2
```{r}
#Describe the raw data: For the homicides raw dataset, it contains 52179 observations and 12 variables (columns), which are respectively uid, reported_date, victim_last, victim_first, victim_race, victim_age, victim_sex, city, state, latitude, longtitude, disposition. There are some NA missing value in latitude and longtitude column. Also, in the columns "race", "age" and "sex" contains data unknown which can indeciate that the person information is still misiing. 

hd = read_csv("homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  na.omit() %>% 
   mutate(city_state = str_c(city,",", state), 
         homicides = case_when(disposition == "Closed without arrest" ~ "unsolved homicides", disposition == "Open/No arrest" ~ "unsolved homicides", disposition == "Closed by arrest" ~ "solved homicides")) %>%
  filter(city_state != "TulsaAL") %>% 
  relocate(city_state)


hd %>% 
  group_by(city_state, homicides) %>% 
  count() %>% 
  knitr::kable()
```

estimate the unsolved proportion of homicides in Baltimore, MD
```{r}
Baltimore = hd %>%
  filter(city_state == "Baltimore,MD") %>%  
  summarise(
    unsolved = sum(homicides == "unsolved homicides"),
    n = n()
  )

Baltimore_test = 
  prop.test(
    x = Baltimore %>% pull(unsolved),
    n = Baltimore %>% pull(n))

Baltimore_test %>% 
  broom::tidy() 
```

Prop.test for each of the city
```{r}
city_proptest = function(city_df){
  city_summarize = city_df %>%
  summarise(
    unsolved = sum(homicides == "unsolved homicides"),
    n = n())
  
  city_test = 
  prop.test(
    x = city_summarize %>% pull(unsolved),
    n = city_summarize %>% pull(n))
  
  return(city_test)
}
```

Create a tidy dataframe with estimated proportions and CIs for each city
```{r}
nested_df = hd %>%
  nest(alldata = uid:homicides) %>% 
  mutate(
    test_results = map(alldata, city_proptest),
    cleanresults = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, cleanresults) %>% 
  unnest(cleanresults) %>% 
  select(city_state, estimate, starts_with("conf"))
```
Creat the plot
```{r}
nested_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point()+geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Estimate vale among different city with errorbar",
       x = "City(State)",
       y = "Estimate") 
```

Problem 3
t_test function
```{r}
norm_and_t_test = function(mu) {
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = 5),
  )  
    t.test(sim_data, mu =0, conf.level = 0.95, alternative = "two.sided") %>%
    broom::tidy() %>% 
    select(estimate, p.value)
}
```
testing mean=0
```{r}
sim_reuslt_df_0=
  expand_grid(
    true_mean=0,
    iter=1:5000)%>%
  mutate(results=map(true_mean,norm_and_t_test))%>%
  unnest(results)
head(sim_reuslt_df_0)
```

using the function for mean=1,2,3,4,5,6
```{r}
sim_results_df = 
  expand_grid(
    mu = c(1, 2, 3, 4, 5, 6),
    iter = 1:5000) %>% 
  mutate(results = map(mu, norm_and_t_test)) %>% 
  unnest(results)
head(sim_results_df)
```

First plot(mu vs. proportion of reject)
```{r}
mu_prop = sim_results_df %>% 
  mutate(decision = case_when(p.value < 0.05 ~ "reject", p.value >= 0.05 ~ "fail_to_reject")) %>% 
  group_by(mu) %>% 
  summarize(n_obs = n(), prop_reject = sum(decision == "reject") / n_obs * 100)%>%
  ggplot(aes(x = mu, y = prop_reject)) + geom_point() +geom_line(alpha = .5)+labs(title = "Power vs. True mean",x = "True mean", y = "Power")+scale_x_continuous(breaks = 1:6)

mu_prop
```

Second graph (true value mu vs. average estimate of mu)
```{r}
true_estimate = sim_results_df %>% 
  mutate(decision = case_when(p.value < 0.05 ~ "reject", p.value >= 0.05 ~ "fail_to_reject")) %>% 
  group_by(mu) %>% 
  summarize(average_estimate = mean(estimate)) %>% 
  ggplot(aes(x = mu, y = average_estimate)) +
  geom_point()+ geom_line(alpha = .5)+ labs(title = "True value mu vs. average estimate of mean",
    x = "True mean",
    y = "Average estimated mean"
  )
true_estimate  
```

Third graph (true mean vs. average estimate of mu only only in samples for which the null was rejected)
```{r}
sd = sim_results_df %>% 
  mutate(decision = case_when(p.value < 0.05 ~ "reject", p.value >= 0.05 ~ "fail_to_reject")) %>% 
  filter(decision == "reject") %>%
  group_by(mu) %>% 
  summarize(average_estimate = mean(estimate), null_reject = sum(p.value)) %>% 
  ggplot(aes(x = mu, y = average_estimate))+ geom_point()+
  geom_smooth()+ labs(title="true mean vs. average estimate of mu only only in samples for which the null was rejected",
         x="true mean",
         y="estimated mean")
sd
```


